Identifying and correcting for misspecifications\\in GWAS summary statistics for polygenic scores

### 2022-02-04 paper/paper-misspec.tex
add mismatched LD

>>>>

\subsection{Mismatch between LD reference and GWAS summary statistics}

Here we design simulations to understand the impact of using a mismatched LD reference panel, e.g.\ that comes from a different population compared to the one used to compute the GWAS summary statistics.
We use the same simulation setup as before (Methods).
In addition, we design an alternative reference panel based on 10,000 individuals from South Europe by using the ``Italy'' center defined in \cite{prive2021high}.
Averaged over 10 simulations, when using an ``alternative'' LD reference panel instead of well-matched one, squared correlations between the polygenic scores and the simulated phenotypes drop from 0.174 to 0.167 for lassosum2, from 0.168 to 0.147 for LDpred2(-grid), from 0.174 to 0.169 for LDpred2-low-h2, from 0.143 to 0.139 for LDpred2-auto, from 0.162 to 0.146 for LDpred2-auto-rob, and from 0.144 to 0.140 for LDpred2-inf (Figure \ref{fig:simu-altpop}).
Defining LD blocks in these two LD matrices always helps, but do not improve performance by much when using the alternative LD.
